---
title: "ELToD Results"
author: "Amar Sarvepalli"
date: "July 27, 2017"
output:
  flexdashboard::flex_dashboard:
    theme: united
    keep_md: yes
  navbar:
  - align: left
    title: About
  source_code: embed
---


```{r setup, include=FALSE}

#======================================================================
# Check and install libraries 
#======================================================================
required_packages <- c("knitr", "flexdashboard","dplyr", "tidyr", "plotly", 
                       "DT", "leaflet", "data.table", "XLConnect", "foreign")

check_packages <- required_packages %in% rownames(installed.packages())
missing_packages <- required_packages[check_packages == FALSE]

if (length(missing_packages) > 0) {
  install.packages(missing_packages)
}

sapply(required_packages, library, character.only = TRUE)


# Set chunk options
opts_knit$set(root.dir=normalizePath('../'))
opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	fig.path = "figures/",
  dev = 'png',
  fig.keep = 'all',
	dev.args=list(type="cairo")
)


options(DT.options = list(pageLength = 5, language = list(search = 'Filter:')),
        initComplete = JS(
        "function(settings, json) {",
        "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",
         "}"),
        searchHighlight = TRUE, filter = 'none')

```


```{r User_Settings, echo=FALSE, message=FALSE, warning=FALSE}
#======================================================================
# Read data files
#======================================================================
# scenario path settings
proj_path <- "C:/projects/R-projects/ELToD_Visualization/Data/Veterans"
dir.ELToD <- "ELToD Results"
dir.Analysis <- "Analysis"
policy <- c("oldPolicy", "newPolicy")
scenarios <- c("Y2020Rev", "Y2040Rev")
Years     <- c(2020, 2040)

# filenames and pull links
filenames <- paste0("VOL",c(1:24),".csv")
pull_link <- "Pull_Link_Dir.csv"

# output excel files, segment starting rows
excel_template <- "Template.xlsx"
segments <- c(1,2,3)
seg_data_start_rows <- c(6, 51, 96)
sheet_name = "Output"
old_outfiles <- c("Output_2020A1.xlsx", "Output_2040A1.xlsx")
new_outfiles <- c("Output_2020A2.xlsx", "Output_2040A2.xlsx")

# A choice to read data from excel spreadsheets instead of standard ELToD outputs
export_summaries_to_excel <- TRUE
read_from_excel <- FALSE

# Declare all full paths here
file_path <- paste(proj_path, dir.ELToD, sep = "/")
analysis_path <- paste(proj_path, dir.Analysis, sep = "/")
pull_link_full_path <- paste(file_path, pull_link, sep="/") 
excel_template_full_path <- paste(file_path, excel_template, sep="/") 

```


```{r read_model_outputs}

  # Read ELToD raw files
  if (!read_from_excel) {
    source('Read_ELToD_Outputs.R')
    
    # Export ELToD Sumamries to Spreadsheets
    if(export_summaries_to_excel){
      source('Export_ELTOD_Output.R')
      
    }
  } else {
    
    # Read ELToD Summaries from Anslysis Spreadsheet
    source('Read_ELTOD_Summaries.R')
  }
   

```


```{r plot volume function w animation}
accumulate_by <- function(dat, var) {
  var <- lazyeval::f_eval(var, dat)
  lvls <- plotly:::getLevels(var)
  dats <- lapply(seq_along(lvls), function(x) {
    cbind(dat[var %in% lvls[seq(1, x)], ], frame = lvls[[x]])
  })
  dplyr::bind_rows(dats)
}

# TODO: 
# Do both old and new plots in the same layout but as two graphs to use same Y-axis
plot_volumes_ami <- function(df) {
  df %>% 
  plot_ly(
    x = ~Hour,
    y = ~Volume,    
    split = ~Segment,
    frame = ~frame,
    type = 'scatter',
    mode = 'lines',
    showlegend = T
  )  %>%
  layout(title = "Volumes by Segment",
         updatemenus = list(
            list(
              type = "buttons",
              y = 0.8,
              buttons = list(
        
                list(method = "restyle",
                     args = list("type", "bar"),
                     label = "Bar"),
        
                list(method = "restyle",
                     args = list("type", "scatter"),
                     label = "Scatter")
                )
              )
            ),
          
         # Add LOS-B, LOS-C Highlighers
          shapes = list(
               list(type = "rect",
                    fillcolor = "orange", line = list(color = "orange"), opacity = 0.15,
                    x0 = "8", x1 = "10", xref = "x",
                    y0 = 0, y1 = 1500, yref = "y"),
               list(type = "rect",
                    fillcolor = "orange", line = list(color = "orange"), opacity = 0.15,
                    x0 = "16", x1 = "18", xref = "x",
                    y0 = 0, y1 = 1500, yref = "y")             
               ),
         
         # Add AM and PM Peaks 
         annotations = list( 
           list(x = 9, y = -50, text = " AM: 8:00 - 10:00 ", 
                font = list(family = 'Arial',color = 'rgba(49,130,189, 1)', size = 12), 
                showarrow = FALSE),
           list(x = 17, y = -50, text = " PM: 16:00 - 18:00 ", 
                font = list(family = 'Arial', color = 'rgba(49,130,189, 1)', size = 12), 
                showarrow = FALSE)
         ),
         
         yaxis = list(domain = c(0, 1500))
         
     ) %>%
  animation_opts(
    frame = 60, 
    transition = 0, 
    redraw = FALSE
  ) 
}

  
```


```{r plot volume function}

# TODO: 
# Do both old and new plots in the same layout but as two graphs to use same Y-axis

plot_volumes <- function(df, max_volume, isGL) {
  
   if(isGL){
     ls_colors <-  c('rgb(208,28,139)',
                   'rgb(241,182,218)',
                   'rgb(184,225,134)',
                   'rgb(77,172,38)')
   } else {
      ls_colors <-  c('rgb(228,26,28)',
                   'rgb(55,126,184)',
                   'rgb(77,175,74)',
                   'rgb(152,78,163)')
   }
   
  
  # create color list
  for (c in 1:length(ls_colors)){
     ifelse( c == 1, bar_colors <- rep(ls_colors[c],24), bar_colors <- c(bar_colors, rep(ls_colors[c],24)))
  }
  
  df %>% 
  plot_ly(
    x = ~Hour,
    y = ~Volume,    
    split = ~Segment,
    marker = list(color = bar_colors,
                  line = list(color = bar_colors)),
    type = 'bar',
    mode = 'lines',
    showlegend = T
  )  %>%
  layout(title = "Volumes by Segment",
         
         # Add LOS-B, LOS-C Highlighers
          shapes = list(
               list(type = "rect",
                    fillcolor = "orange", line = list(color = "orange"), opacity = 0.15,
                    x0 = "8", x1 = "10", xref = "x",
                    y0 = 0, y1 = max_volume, yref = "y"),
               list(type = "rect",
                    fillcolor = "orange", line = list(color = "orange"), opacity = 0.15,
                    x0 = "16", x1 = "18", xref = "x",
                    y0 = 0, y1 = max_volume, yref = "y")             
               ),
         
         # Add AM and PM Peaks 
         annotations = list( 
           list(x = 9, y = -50, text = " AM: 8:00 - 10:00 ", 
                font = list(family = 'Arial',color = 'rgba(49,130,189, 1)', size = 12), 
                showarrow = FALSE),
           list(x = 17, y = -50, text = " PM: 16:00 - 18:00 ", 
                font = list(family = 'Arial', color = 'rgba(49,130,189, 1)', size = 12), 
                showarrow = FALSE)
         ),
         
         yaxis = list(range = c(0, max_volume))
     )
}

  
```


Year 2020 {data-navmenu="EL Volumes"}   
=====================================
Row
-------------------------------------
    
### 2020: EL Old Policy 
    Old Policy Definition: Where LOS-A is charged

```{r Old policy 2020, include=TRUE}
old_policy_2020 <- df %>%
              filter(Year == 2020, Policy == "oldPolicy") %>%
              select(Seg, Hour, EL_SB_VOL, EL_NB_VOL ) %>%
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>%
              plot_volumes(1000,FALSE)

# Plot Old Polciy Volumes
old_policy_2020
```

Row
-------------------------------------
### 2020: EL New Policy
    New Policy Definition: Where LOS-A is NOT charged
```{r New policy 2020}
# Plot New Policy Volumes
new_policy_2020 <- df %>%
              filter(Year == 2020, Policy == "newPolicy") %>%
              select(Seg, Hour, EL_SB_VOL, EL_NB_VOL ) %>%
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>%
              plot_volumes(1000,FALSE)

new_policy_2020

```



Year 2040 {data-navmenu="EL Volumes"}   
=====================================
Row
-------------------------------------
    
### 2040: EL Old Policy 
    Old Policy Definition: Where LOS-A is charged    
```{r Old policy 2040}
old_policy_2040 <- df %>% 
              filter(Year == 2040, Policy == "oldPolicy") %>%
              select(Seg, Hour, EL_SB_VOL, EL_NB_VOL ) %>% 
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>% 
              plot_volumes(2000,FALSE)

# Plot Old Policy Volumes
old_policy_2040
```
   
Row
-------------------------------------
### 2040: EL New Policy 
    New Policy Definition: Where LOS-A is NOT charged 
```{r New policy 2040}
# Plot New Policy Volumes
new_policy_2040 <- df %>% 
              filter(Year == 2040, Policy == "newPolicy") %>%
              select(Seg, Hour, EL_SB_VOL, EL_NB_VOL ) %>% 
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>%
              plot_volumes(2000,FALSE)

new_policy_2040 
```



Year 2020 {data-navmenu="GL Volumes"}   
=====================================
Row
-------------------------------------
    
### 2020: GL Old Policy 
    Old Policy Definition: Where LOS-A is charged

```{r GL Old policy 2020}
old_policy_2020 <- df %>%
              filter(Year == 2020, Policy == "oldPolicy") %>%
              select(Seg, Hour, GU_SB_VOL, GU_NB_VOL ) %>%
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>%
              plot_volumes(4000,TRUE)

# Plot Old Polciy Volumes
old_policy_2020
```

Row
-------------------------------------
### 2020: GL New Policy
    New Policy Definition: Where LOS-A is NOT charged
```{r GL New policy 2020}
# Plot New Policy Volumes
new_policy_2020 <- df %>%
              filter(Year == 2020, Policy == "newPolicy") %>%
              select(Seg, Hour, GU_SB_VOL, GU_NB_VOL ) %>%
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>%
              plot_volumes(4000,TRUE)

new_policy_2020

```



Year 2040 {data-navmenu="GL Volumes"}   
=====================================
Row
-------------------------------------
    
### 2040: GL Old Policy 
    Old Policy Definition: Where LOS-A is charged    
```{r GL Old policy 2040}
old_policy_2040 <- df %>% 
              filter(Year == 2040, Policy == "oldPolicy") %>%
              select(Seg, Hour, GU_SB_VOL, GU_NB_VOL ) %>% 
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>% 
              plot_volumes(6000,TRUE)

# Plot Old Policy Volumes
old_policy_2040
```
   
Row
-------------------------------------
### 2040: GL New Policy 
    New Policy Definition: Where LOS-A is NOT charged 
```{r GL New policy 2040}
# Plot New Policy Volumes
new_policy_2040 <- df %>% 
              filter(Year == 2040, Policy == "newPolicy") %>%
              select(Seg, Hour, GU_SB_VOL, GU_NB_VOL ) %>% 
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>% 
              plot_volumes(6000,TRUE)

new_policy_2040
```


Summary {data-navmenu="LOS"} 
=====================================


```{r plot v/c}

plot_voc <- function(df) {
  df %>% 
  plot_ly(
    x = ~Hour,
    y = ~VC,    
    type = 'scatter',
    mode = 'lines',
    color = ~direction,
    showlegend = T
  )  %>%

  layout(title = "V/C by Lane Type",

          # Add LOS-B, LOS-C Highlighers
          shapes = list(
               list(type = "rect",
                    fillcolor = "yellow", line = list(color = "yellow"), opacity = 0.15,
                    x0 = "0", x1 = "24", xref = "x",
                    y0 = 0.0, y1 = 0.3, yref = "y"),
               list(type = "rect",
                    fillcolor = "green", line = list(color = "green"), opacity = 0.15,
                    x0 = "0", x1 = "24", xref = "x",
                    y0 = 0.3, y1 = 0.5, yref = "y"),
               list(type = "rect",
                    fillcolor = "orange", line = list(color = "orange"), opacity = 0.15,
                    x0 = "0", x1 = "24", xref = "x",
                    y0 = 0.5, y1 = 0.75, yref = "y")
               ),
         
         # Add LOS 
         annotations = list( 
           list(x = 3, y = 0.15, text = " LOS A = V/C below 0.3 ", 
                font = list(family = 'Arial',color = 'rgba(49,130,189, 1)', size = 12), 
                showarrow = FALSE),
           list(x = 3, y = 0.4, text = " LOS B = V/C 0.3 to 0.5 ", 
                font = list(family = 'Arial', color = 'rgba(49,130,189, 1)', size = 12), 
                showarrow = FALSE),
           list(x = 3, y = 0.6, text = " LOS C = V/C above 0.5 ", 
                font = list(family = 'Arial', color = 'rgba(49,130,189, 1)', size = 12), 
                showarrow = FALSE)
         )
         
    ) 
}
```


```{r V/C LOS plots, message=FALSE}

# old policy 2020 seg 1
df_old_policy_2020_seg1 <- df %>% 
              filter(Year == 2020, Policy == "oldPolicy", Seg == 1) %>%
              select(Hour, GU_NB_VC_RATIO, GU_SB_VC_RATIO, 
                     EL_NB_VC_RATIO, EL_SB_VC_RATIO)

old_policy_2020_seg1 <- df_old_policy_2020_seg1 %>% 
              gather( -Hour, key = direction, value = VC) %>%
              select(Hour, direction, VC ) %>% 
              plot_voc()


# old policy 2020 seg 2
df_old_policy_2020_seg2 <- df %>% 
              filter(Year == 2020, Policy == "oldPolicy", Seg == 2) %>%
              select(Hour, GU_NB_VC_RATIO, GU_SB_VC_RATIO, 
                     EL_NB_VC_RATIO, EL_SB_VC_RATIO)

old_policy_2020_seg2 <- df_old_policy_2020_seg2 %>%
              gather( -Hour, key = direction, value = VC) %>%
              select(Hour, direction, VC ) %>% 
              plot_voc()


# new policy 2020 seg 1
df_new_policy_2020_seg1 <- df %>% 
              filter(Year == 2020, Policy == "newPolicy", Seg == 1) %>%
              select(Hour, GU_NB_VC_RATIO, GU_SB_VC_RATIO, 
                     EL_NB_VC_RATIO, EL_SB_VC_RATIO) 

new_policy_2020_seg1 <- df_new_policy_2020_seg1 %>%
              gather( -Hour, key = direction, value = VC) %>%
              select(Hour, direction, VC ) %>% 
              plot_voc()


# new policy 2020 seg 2
df_new_policy_2020_seg2 <- df %>% 
              filter(Year == 2020, Policy == "newPolicy", Seg == 2) %>%
              select(Hour, GU_NB_VC_RATIO, GU_SB_VC_RATIO, 
                     EL_NB_VC_RATIO, EL_SB_VC_RATIO)  

new_policy_2020_seg2 <- df_new_policy_2020_seg2  %>%            
              gather( -Hour, key = direction, value = VC) %>%
              select(Hour, direction, VC ) %>% 
              plot_voc()
```


```{r LOS summaries}
### 2040: Old Policy Segment 2: Anderson
los_vol <- df %>% 
         select(Year, Policy, Seg, Hour, 
                GU_NB_VOL, GU_SB_VOL, EL_NB_VOL, EL_SB_VOL,
                EL_NB_VC_RATIO, EL_SB_VC_RATIO) %>%
         gather(-Year, -Policy, -Seg, -Hour, -GU_NB_VOL, -GU_SB_VOL, -EL_NB_VOL, -EL_SB_VOL,
                key = Dir, value = vc) %>%
         mutate(EL_NB_VOL = ifelse(Dir == "EL_NB_VC_RATIO", EL_NB_VOL, 0),
                EL_SB_VOL = ifelse(Dir == "EL_SB_VC_RATIO", EL_SB_VOL, 0),
                GU_NB_VOL = ifelse(Dir == "EL_NB_VC_RATIO", GU_NB_VOL, 0),
                GU_SB_VOL = ifelse(Dir == "EL_SB_VC_RATIO", GU_SB_VOL, 0),
                GU_TOT =  GU_NB_VOL + GU_SB_VOL,
                EL_TOT = EL_NB_VOL + EL_SB_VOL,
                TOT = GU_TOT + EL_TOT,
                LOS = ifelse(vc < 0.3, "A",
                             ifelse(vc >= 0.5, "C", "B")
                             )
                ) %>%
         group_by(Year, Policy, Seg, LOS) %>%
         summarise(EL = sum(EL_TOT),
                   Corridor = sum(TOT),
                   EL_Share = EL / Corridor
                   )%>%
         arrange(Year, Policy)

los_EL <- los_vol %>% 
          select(-EL_Share, -Corridor) %>%
          spread(Policy, EL) %>%
          mutate_each(funs(replace(.,is.na(.),0)))

los_EL_shares <- los_vol %>% 
          select(-EL, -Corridor) %>%
          spread(Policy, EL_Share) %>%
          mutate_each(funs(replace(.,is.na(.),0)))

# Compute trips paying by LOS
los_paying <- los_vol %>% 
          select(-EL_Share, -Corridor) %>%
          spread(Policy, EL) %>%
          mutate_each(funs(replace(.,is.na(.),0))) %>%
          mutate(old_pay = oldPolicy,
                 new_pay = ifelse(LOS == "A", 0, newPolicy)) %>%
          select(Year, Seg, LOS, oldPolicy = old_pay, newPolicy = new_pay)
          

plot_los <- function(df){
          df %>% 
          plot_ly(x = ~LOS, y = ~oldPolicy, name = 'Old Policy', 
                  type = 'bar', marker = list(color = 'rgb(173, 255, 6)')) %>%
          add_trace(y = ~newPolicy, name = 'New Policy', 
                    marker = list(color = 'rgba(255, 10, 255)')) %>%
          layout(yaxis = list(title = ' '), barmode = 'group')
}

 

```

Column {data-width=350}
-------------------------------------
### Volumes by LOS 
```{r} 
los_EL_all <- los_EL %>% 
              group_by(Year, LOS) %>% 
              summarise_each(funs(sum))%>% 
              select(-Seg)  %>%
              gather(-Year, -LOS, key = Policy, value = trips) %>% 
              spread(LOS, trips) %>% 
              mutate_each(funs(replace(.,is.na(.),0))) %>%
              mutate(Total = A + B + C)

datatable(
  los_EL_all, 
  options = list(dom  = 't'),
  # extensions = 'Buttons', options = list(
  #   dom = 'Bfrtip',
  #   buttons = c('copy', 'excel')
  # ),
   rownames = FALSE
)

```

### Trips paying
```{r} 
los_paying_all <- los_paying %>% 
              group_by(Year, LOS) %>% 
              summarise_each(funs(sum))%>% 
              select(-Seg) %>%
              gather(-Year, -LOS, key = Policy, value = trips) %>% 
              spread(LOS, trips) %>% 
              mutate_each(funs(replace(.,is.na(.),0))) %>%
              mutate(Total = A + B + C)

datatable(
  los_paying_all, 
  options = list(dom  = 't'),
  # extensions = 'Buttons', options = list(
  #   dom = 'Bfrtip',
  #   buttons = c('copy', 'excel')
  # ),
  rownames = FALSE
)

```



```{r}

x <- los_EL %>% 
     gather(-Year, -LOS, -Seg, key = Policy, value = trips) %>% 
     spread(LOS, trips) %>% 
     mutate_each(funs(replace(.,is.na(.),0))) %>%
     mutate(Total = A + B + C) %>%
     arrange(Policy, Year, Seg) %>% 
     ungroup()

addTotals <- function(df, policy, year){
   y <- df %>% 
        filter(Policy == policy, Year == year) %>%
        mutate(Segment = ifelse(Seg == 1, "Sugarwood", "Anderson")) %>%
        select(-Seg, -Policy, -Year, Segment, A, B, C, Total)
   
   z <- colSums(y[2:5])
   yz <- rbind(y, c("Total", z[2:5]))
   return(yz)
}

# Old policy
x %>% 
  filter(Policy == "oldPolicy", Year == 2020) %>% 
  addTotals()

  mutate(Segment = ifelse(1, "Sugarwood", "Anderson"))

x <- x %>% summarise()

datatable(x, options = list(dom = 't')) %>%
  formatStyle('Sepal.Length',  color = 'red', backgroundColor = 'orange', fontWeight = 'bold')

```


Column {data-width=700}
-------------------------------------
### Map of Veterans Expressway

```{r Map}
# veteran_shp <- rgdal::readOGR(paste(file_path, shape_file, sep = "\\"),
#                   layer = "Veterans_v2", GDAL1_integer64_policy = TRUE)

map <- leaflet() %>%
       addTiles() %>%
       setView(lng = -82.5381, lat = 28.0679, zoom = 11)

map
```


Year 2020: Sugarwood {data-navmenu="LOS"} 
=====================================

Column {data-width=350}
-------------------------------------
### Level of Service (LOS) 

* LOS A: V/C below 0.3
* LOS B: V/C between 0.3 and 0.5
* LOS C: V/C above 0.5

### EL Volumes
```{r}
 los_EL %>% 
 filter(Year == 2020, Seg == 1) %>% plot_los()

```

### EL Shares
```{r}
 los_EL_shares %>%
 filter(Year == 2020, Seg == 1) %>% plot_los()

```

### Trips Paying
```{r}
 los_paying %>%
 filter(Year == 2020, Seg == 1) %>% plot_los()

```



Column
-------------------------------------
    
### 2020: Old Policy Segment 1: Sugarwood

```{r old_policy_2020_seg1}
old_policy_2020_seg1

```


### 2020: New Policy Segment 1: Sugarwood

```{r new_policy_2020_seg1 }
new_policy_2020_seg1

```



Year 2020: Anderson {data-navmenu="LOS"} 
=====================================

Column {data-width=350}
-------------------------------------
### Level of Service (LOS) 

* LOS A: V/C below 0.3
* LOS B: V/C between 0.3 and 0.5
* LOS C: V/C above 0.5

### EL Volumes
```{r}
 los_EL %>%
 filter(Year == 2020, Seg == 2) %>% plot_los()

```

### EL Shares
```{r}
 los_EL_shares %>%
 filter(Year == 2020, Seg == 2) %>% plot_los()

```

### Trips Paying
```{r}
 los_paying %>%
 filter(Year == 2020, Seg == 2) %>% plot_los()

```



Column
-------------------------------------
    
### 2020: Old Policy Segment 2: Anderson

```{r old_policy_2020_seg2}
old_policy_2020_seg2

```


### 2020: New Policy Segment 2: Anderson

```{r new_policy_2020_seg2 }
new_policy_2020_seg2

```


Year 2040: Sugarwood {data-navmenu="LOS"} 
=====================================

```{r 2040 V/C LOS plots, message=FALSE}

# old policy 2040 seg 1
df_old_policy_2040_seg1 <- df %>% 
              filter(Year == 2040, Policy == "oldPolicy", Seg == 1) %>%
              select(Hour, GU_NB_VC_RATIO, GU_SB_VC_RATIO, 
                     EL_NB_VC_RATIO, EL_SB_VC_RATIO)

old_policy_2040_seg1 <- df_old_policy_2040_seg1 %>% 
              gather( -Hour, key = direction, value = VC) %>%
              select(Hour, direction, VC ) %>% 
              plot_voc()


# old policy 2040 seg 2
df_old_policy_2040_seg2 <- df %>% 
              filter(Year == 2040, Policy == "oldPolicy", Seg == 2) %>%
              select(Hour, GU_NB_VC_RATIO, GU_SB_VC_RATIO, 
                     EL_NB_VC_RATIO, EL_SB_VC_RATIO)

old_policy_2040_seg2 <- df_old_policy_2040_seg2 %>%
              gather( -Hour, key = direction, value = VC) %>%
              select(Hour, direction, VC ) %>% 
              plot_voc()


# new policy 2040 seg 1
df_new_policy_2040_seg1 <- df %>% 
              filter(Year == 2040, Policy == "newPolicy", Seg == 1) %>%
              select(Hour, GU_NB_VC_RATIO, GU_SB_VC_RATIO, 
                     EL_NB_VC_RATIO, EL_SB_VC_RATIO) 

new_policy_2040_seg1 <- df_new_policy_2040_seg1 %>%
              gather( -Hour, key = direction, value = VC) %>%
              select(Hour, direction, VC ) %>% 
              plot_voc()


# new policy 2040 seg 2
df_new_policy_2040_seg2 <- df %>% 
              filter(Year == 2040, Policy == "newPolicy", Seg == 2) %>%
              select(Hour, GU_NB_VC_RATIO, GU_SB_VC_RATIO, 
                     EL_NB_VC_RATIO, EL_SB_VC_RATIO)  

new_policy_2040_seg2 <- df_new_policy_2040_seg2  %>%            
              gather( -Hour, key = direction, value = VC) %>%
              select(Hour, direction, VC ) %>% 
              plot_voc()
```

Column {data-width=350}
-------------------------------------
### Level of Service (LOS) 

* LOS A: V/C below 0.3
* LOS B: V/C between 0.3 and 0.5
* LOS C: V/C above 0.5

### EL Volumes
```{r}
 los_EL %>%
 filter(Year == 2040, Seg == 1) %>% plot_los()

```

### EL Shares
```{r}
 los_EL_shares %>%
 filter(Year == 2040, Seg == 1) %>% plot_los()

```

### Trips Paying
```{r}
 los_paying %>%
 filter(Year == 2040, Seg == 1) %>% plot_los()

```

Column 
-------------------------------------
    
### 2040: Old Policy Segment 1: Sugarwood

```{r old_policy_2040_seg1}
old_policy_2040_seg1
```


### 2040: New Policy Segment 1: Sugarwood

```{r new_policy_2040_seg1 }
new_policy_2040_seg1

```



Year 2040: Anderson {data-navmenu="LOS"} 
=====================================

Column {data-width=350}
-------------------------------------
### Level of Service (LOS) 

* LOS A: V/C below 0.3
* LOS B: V/C between 0.3 and 0.5
* LOS C: V/C above 0.5

### EL Volumes
```{r}
 los_EL %>%
 filter(Year == 2040, Seg == 2) %>% plot_los()

```

### EL Shares
```{r}
 los_EL_shares %>%
 filter(Year == 2040, Seg == 2) %>% plot_los()

```

### Trips Paying
```{r}
 los_paying %>%
 filter(Year == 2040, Seg == 2) %>% plot_los()

```


Column 
-------------------------------------

### 2040: Old Policy Segment 2: Anderson

```{r old_policy_2040_seg2}
old_policy_2040_seg2

```


### 2040: New Policy Segment 2: Anderson

```{r new_policy_2040_seg2 }
new_policy_2040_seg2

```


