---
title: "ELToD Results"
author: "Amar Sarvepalli"
date: "July 27, 2017"
output:
  flexdashboard::flex_dashboard:
    theme: united
    keep_md: yes
  navbar:
  - align: left
    title: About
  source_code: embed
---


```{r setup, include=FALSE}

#======================================================================
# Check and install libraries 
#======================================================================
  required_packages <- c("knitr", "flexdashboard",
                         "dplyr", "tidyr", 
                         "DT", "data.table", "XLConnect", "foreign",
                         "plotly", "rgdal", "leaflet")
  
  check_packages <- required_packages %in% rownames(installed.packages())
  missing_packages <- required_packages[check_packages == FALSE]
  
  if (length(missing_packages) > 0) {
    install.packages(missing_packages)
  }
  
  sapply(required_packages, library, character.only = TRUE)
  
  
  # Set chunk options
  opts_knit$set(root.dir=normalizePath('../'))
  opts_chunk$set(
  	echo = FALSE,
  	message = FALSE,
  	warning = FALSE,
  	fig.path = "figures/",
    dev = 'png',
    fig.keep = 'all',
  	dev.args=list(type="cairo")
  )
  
  
  options(DT.options = list(pageLength = 5, language = list(search = 'Filter:')),
          initComplete = JS(
          "function(settings, json) {",
          "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",
           "}"),
          searchHighlight = TRUE, filter = 'none')

```


```{r User_Settings, echo=FALSE, message=FALSE, warning=FALSE}
#======================================================================
# Read data files
#======================================================================
  # Path settings
  dir_path     <- "C:/projects/R-projects/ELToD_Visualization"
  dir.ELToD    <- "ELToD Results"
  dir.Analysis <- "Analysis"
  dir.Shape    <- "Project_Shape"
  
  # Scenario settings
  policy    <- c("oldPolicy", "newPolicy")
  scenarios <- c("Y2020Rev", "Y2040Rev")
  Years     <- c(2020, 2040)
  
  # filenames and pull links
  filenames <- paste0("VOL",c(1:24),".csv")
  pull_link <- "Pull_Link_Dir.csv"
  
  # output excel files, segment starting rows
  excel_template <- "Template.xlsx"
  segments <- c(1,2,3)
  seg_data_start_rows <- c(6, 51, 96)
  sheet_name = "Output"
  old_outfiles <- c("Output_2020A1.xlsx", "Output_2040A1.xlsx")
  new_outfiles <- c("Output_2020A2.xlsx", "Output_2040A2.xlsx")
  
  # Excel Summary file
  # A choice to read data from excel spreadsheets instead of standard ELToD outputs
  read_from_excel <- TRUE
  
  # when read_from_excel is false, should it write to excel summaries
  export_summaries_to_excel <- FALSE
  
  # excel_summary_file <- "Result_Veterans_2017-0818_2020_uses_original_hourly_distribution.xlsx"
  
  # Display project on map (Dashboard 'Summary' tab)
  display_Project <- TRUE
  shape_file <- "Veterans_v2.shp"
  

```


```{r generate_input_file_fullpaths}

  # Declare all sub-directory paths
  proj_path <- paste0(dir_path,"/Data/Veterans")
  file_path <- paste(proj_path, dir.ELToD, sep = "/")
  analysis_path <- paste(proj_path, dir.Analysis, sep = "/")
  shape_path <- paste(proj_path, dir.Shape, sep = "/")
  
  # Input file full-paths
  pull_link_full_path <- paste(file_path, pull_link, sep="/") 
  excel_template_full_path <- paste(file_path, excel_template, sep="/") 
  shape_file_full_path <- paste(shape_path, shape_file, sep="/") 
  
  # excel_summary_full_path <- paste(analysis_path, excel_summary_file, sep ="/") 

```



```{r read_model_outputs}

  # Read ELToD raw files
  if (!read_from_excel) {
    source(paste0(dir_path,'/R/Read_ELToD_Outputs.R'))
    
    # Export ELToD Sumamries to Spreadsheets
    if(export_summaries_to_excel){
      source(paste0(dir_path,'/R/Export_ELToD_Output.R'))
      
    }
  } else {
    
    # Read ELToD Summaries from Anslysis Spreadsheet
    source(paste0(dir_path,'/R/Read_ELToD_Summaries.R'))
  }
   

```


```{r plot volume function}
   # load function to animate
   source(paste0(dir_path,'/R/Function_To_Plot_Volumes.R'))
```


Year 2020 {data-navmenu="EL Volumes"}   
=====================================
Row
-------------------------------------
    
### 2020: EL Old Policy 
    Old Policy Definition: Where LOS-A is charged

```{r Old policy 2020, include=TRUE}
old_policy_2020 <- df %>%
              filter(Year == 2020, Policy == "oldPolicy") %>%
              select(Seg, Hour, EL_SB_VOL, EL_NB_VOL ) %>%
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>%
              plot_volumes(1000,FALSE)

# Plot Old Polciy Volumes
old_policy_2020
```

Row
-------------------------------------
### 2020: EL New Policy
    New Policy Definition: Where LOS-A is NOT charged
```{r New policy 2020}
# Plot New Policy Volumes
new_policy_2020 <- df %>%
              filter(Year == 2020, Policy == "newPolicy") %>%
              select(Seg, Hour, EL_SB_VOL, EL_NB_VOL ) %>%
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>%
              plot_volumes(1000,FALSE)

new_policy_2020

```



Year 2040 {data-navmenu="EL Volumes"}   
=====================================
Row
-------------------------------------
    
### 2040: EL Old Policy 
    Old Policy Definition: Where LOS-A is charged    
```{r Old policy 2040}
old_policy_2040 <- df %>% 
              filter(Year == 2040, Policy == "oldPolicy") %>%
              select(Seg, Hour, EL_SB_VOL, EL_NB_VOL ) %>% 
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>% 
              plot_volumes(2000,FALSE)

# Plot Old Policy Volumes
old_policy_2040
```
   
Row
-------------------------------------
### 2040: EL New Policy 
    New Policy Definition: Where LOS-A is NOT charged 
```{r New policy 2040}
# Plot New Policy Volumes
new_policy_2040 <- df %>% 
              filter(Year == 2040, Policy == "newPolicy") %>%
              select(Seg, Hour, EL_SB_VOL, EL_NB_VOL ) %>% 
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>%
              plot_volumes(2000,FALSE)

new_policy_2040 
```



Year 2020 {data-navmenu="GL Volumes"}   
=====================================
Row
-------------------------------------
    
### 2020: GL Old Policy 
    Old Policy Definition: Where LOS-A is charged

```{r GL Old policy 2020}
old_policy_2020 <- df %>%
              filter(Year == 2020, Policy == "oldPolicy") %>%
              select(Seg, Hour, GU_SB_VOL, GU_NB_VOL ) %>%
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>%
              plot_volumes(4000,TRUE)

# Plot Old Polciy Volumes
old_policy_2020
```

Row
-------------------------------------
### 2020: GL New Policy
    New Policy Definition: Where LOS-A is NOT charged
```{r GL New policy 2020}
# Plot New Policy Volumes
new_policy_2020 <- df %>%
              filter(Year == 2020, Policy == "newPolicy") %>%
              select(Seg, Hour, GU_SB_VOL, GU_NB_VOL ) %>%
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>%
              plot_volumes(4000,TRUE)

new_policy_2020

```



Year 2040 {data-navmenu="GL Volumes"}   
=====================================
Row
-------------------------------------
    
### 2040: GL Old Policy 
    Old Policy Definition: Where LOS-A is charged    
```{r GL Old policy 2040}
old_policy_2040 <- df %>% 
              filter(Year == 2040, Policy == "oldPolicy") %>%
              select(Seg, Hour, GU_SB_VOL, GU_NB_VOL ) %>% 
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>% 
              plot_volumes(6000,TRUE)

# Plot Old Policy Volumes
old_policy_2040
```
   
Row
-------------------------------------
### 2040: GL New Policy 
    New Policy Definition: Where LOS-A is NOT charged 
```{r GL New policy 2040}
# Plot New Policy Volumes
new_policy_2040 <- df %>% 
              filter(Year == 2040, Policy == "newPolicy") %>%
              select(Seg, Hour, GU_SB_VOL, GU_NB_VOL ) %>% 
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>% 
              plot_volumes(6000,TRUE)

new_policy_2040
```


Summary {data-navmenu="LOS"} 
=====================================


```{r plot v/c}
  # Function to plot v/c ratios
  source(paste0(dir_path,'/R/Function_To_Plot_VoC.R'))
```


```{r V/C LOS plots, message=FALSE}

# old policy 2020 seg 1
df_old_policy_2020_seg1 <- df %>% 
              filter(Year == 2020, Policy == "oldPolicy", Seg == 1) %>%
              select(Hour, GU_NB_VC_RATIO, GU_SB_VC_RATIO, 
                     EL_NB_VC_RATIO, EL_SB_VC_RATIO)

old_policy_2020_seg1 <- df_old_policy_2020_seg1 %>% 
              gather( -Hour, key = direction, value = VC) %>%
              select(Hour, direction, VC ) %>% 
              plot_voc()


# old policy 2020 seg 2
df_old_policy_2020_seg2 <- df %>% 
              filter(Year == 2020, Policy == "oldPolicy", Seg == 2) %>%
              select(Hour, GU_NB_VC_RATIO, GU_SB_VC_RATIO, 
                     EL_NB_VC_RATIO, EL_SB_VC_RATIO)

old_policy_2020_seg2 <- df_old_policy_2020_seg2 %>%
              gather( -Hour, key = direction, value = VC) %>%
              select(Hour, direction, VC ) %>% 
              plot_voc()


# new policy 2020 seg 1
df_new_policy_2020_seg1 <- df %>% 
              filter(Year == 2020, Policy == "newPolicy", Seg == 1) %>%
              select(Hour, GU_NB_VC_RATIO, GU_SB_VC_RATIO, 
                     EL_NB_VC_RATIO, EL_SB_VC_RATIO) 

new_policy_2020_seg1 <- df_new_policy_2020_seg1 %>%
              gather( -Hour, key = direction, value = VC) %>%
              select(Hour, direction, VC ) %>% 
              plot_voc()


# new policy 2020 seg 2
df_new_policy_2020_seg2 <- df %>% 
              filter(Year == 2020, Policy == "newPolicy", Seg == 2) %>%
              select(Hour, GU_NB_VC_RATIO, GU_SB_VC_RATIO, 
                     EL_NB_VC_RATIO, EL_SB_VC_RATIO)  

new_policy_2020_seg2 <- df_new_policy_2020_seg2  %>%            
              gather( -Hour, key = direction, value = VC) %>%
              select(Hour, direction, VC ) %>% 
              plot_voc()
```


```{r LOS summaries}
### 2040: Old Policy Segment 2: Anderson
los_vol <- df %>% 
         select(Year, Policy, Seg, Hour, 
                GU_NB_VOL, GU_SB_VOL, EL_NB_VOL, EL_SB_VOL,
                EL_NB_VC_RATIO, EL_SB_VC_RATIO) %>%
         gather(-Year, -Policy, -Seg, -Hour, -GU_NB_VOL, -GU_SB_VOL, -EL_NB_VOL, -EL_SB_VOL,
                key = Dir, value = vc) %>%
         mutate(EL_NB_VOL = ifelse(Dir == "EL_NB_VC_RATIO", EL_NB_VOL, 0),
                EL_SB_VOL = ifelse(Dir == "EL_SB_VC_RATIO", EL_SB_VOL, 0),
                GU_NB_VOL = ifelse(Dir == "EL_NB_VC_RATIO", GU_NB_VOL, 0),
                GU_SB_VOL = ifelse(Dir == "EL_SB_VC_RATIO", GU_SB_VOL, 0),
                GU_TOT =  GU_NB_VOL + GU_SB_VOL,
                EL_TOT = EL_NB_VOL + EL_SB_VOL,
                TOT = GU_TOT + EL_TOT,
                LOS = ifelse(vc < 0.3, "A",
                             ifelse(vc >= 0.5, "C", "B")
                             )
                ) %>%
         group_by(Year, Policy, Seg, LOS) %>%
         summarise(EL = sum(EL_TOT),
                   Corridor = sum(TOT),
                   EL_Share = EL / Corridor
                   )%>%
         arrange(Year, Policy)

los_EL <- los_vol %>% 
          select(-EL_Share, -Corridor) %>%
          spread(Policy, EL) %>%
          mutate_each(funs(replace(.,is.na(.),0)))

los_EL_shares <- los_vol %>% 
          select(-EL, -Corridor) %>%
          spread(Policy, EL_Share) %>%
          mutate_each(funs(replace(.,is.na(.),0)))

# Compute trips paying by LOS
los_paying <- los_vol %>% 
          select(-EL_Share, -Corridor) %>%
          spread(Policy, EL) %>%
          mutate_each(funs(replace(.,is.na(.),0))) %>%
          mutate(old_pay = oldPolicy,
                 new_pay = ifelse(LOS == "A", 0, newPolicy)) %>%
          select(Year, Seg, LOS, oldPolicy = old_pay, newPolicy = new_pay)
          

plot_los <- function(df){
          df %>% 
          plot_ly(x = ~LOS, y = ~oldPolicy, name = 'Old Policy', 
                  type = 'bar', marker = list(color = 'rgb(173, 255, 6)')) %>%
          add_trace(y = ~newPolicy, name = 'New Policy', 
                    marker = list(color = 'rgba(255, 10, 255)')) %>%
          layout(yaxis = list(title = ' '), barmode = 'group')
}


```

Column {data-width=350}
-------------------------------------
### Volumes by LOS 
```{r} 
los_EL_all <- los_EL %>% 
              group_by(Year, LOS) %>% 
              summarise_each(funs(sum))%>% 
              select(-Seg)  %>%
              gather(-Year, -LOS, key = Policy, value = trips) %>% 
              spread(LOS, trips) %>% 
              mutate_each(funs(replace(.,is.na(.),0))) %>%
              mutate(Total = A + B + C)

datatable(
  los_EL_all, 
  options = list(dom  = 't'),
  # extensions = 'Buttons', options = list(
  #   dom = 'Bfrtip',
  #   buttons = c('copy', 'excel')
  # ),
   rownames = FALSE
)

```

### Trips paying
```{r} 
los_paying_all <- los_paying %>% 
              group_by(Year, LOS) %>% 
              summarise_each(funs(sum))%>% 
              select(-Seg) %>%
              gather(-Year, -LOS, key = Policy, value = trips) %>% 
              spread(LOS, trips) %>% 
              mutate_each(funs(replace(.,is.na(.),0))) %>%
              mutate(Total = A + B + C)

datatable(
  los_paying_all, 
  options = list(dom  = 't'),
  # extensions = 'Buttons', options = list(
  #   dom = 'Bfrtip',
  #   buttons = c('copy', 'excel')
  # ),
  rownames = FALSE
)

```



```{r}

x <- los_EL %>% 
     gather(-Year, -LOS, -Seg, key = Policy, value = trips) %>% 
     spread(LOS, trips) %>% 
     mutate_each(funs(replace(.,is.na(.),0))) %>%
     mutate(Total = A + B + C) %>%
     arrange(Policy, Year, Seg) %>% 
     ungroup()


# Old policy
x_old <- x %>% filter(Policy == "oldPolicy", Year == 2020)

datatable(x_old, options = list(dom = 't')) %>%
  formatStyle('A',  color = 'red', backgroundColor = 'orange', fontWeight = 'bold')

# New policy
x_new <- x %>% filter(Policy == "newPolicy", Year == 2020)

datatable(x_new, options = list(dom = 't')) %>%
  formatStyle('A',  color = 'red', backgroundColor = 'orange', fontWeight = 'bold')


```


Column {data-width=700}
-------------------------------------
### Map of Veterans Expressway

```{r Map, message=FALSE, warning=FALSE, echo = FALSE}

source(paste0(dir_path,'/R/Map_Corridor_Location.R'))

```


Year 2020: Sugarwood {data-navmenu="LOS"} 
=====================================

Column {data-width=350}
-------------------------------------
### Level of Service (LOS) 

* LOS A: V/C below 0.3
* LOS B: V/C between 0.3 and 0.5
* LOS C: V/C above 0.5

### EL Volumes
```{r}
 los_EL %>% 
 filter(Year == 2020, Seg == 1) %>% plot_los()

```

### EL Shares
```{r}
 los_EL_shares %>%
 filter(Year == 2020, Seg == 1) %>% plot_los()

```

### Trips Paying
```{r}
 los_paying %>%
 filter(Year == 2020, Seg == 1) %>% plot_los()

```



Column
-------------------------------------
    
### 2020: Old Policy Segment 1: Sugarwood

```{r old_policy_2020_seg1}
old_policy_2020_seg1

```


### 2020: New Policy Segment 1: Sugarwood

```{r new_policy_2020_seg1 }
new_policy_2020_seg1

```



Year 2020: Anderson {data-navmenu="LOS"} 
=====================================

Column {data-width=350}
-------------------------------------
### Level of Service (LOS) 

* LOS A: V/C below 0.3
* LOS B: V/C between 0.3 and 0.5
* LOS C: V/C above 0.5

### EL Volumes
```{r}
 los_EL %>%
 filter(Year == 2020, Seg == 2) %>% plot_los()

```

### EL Shares
```{r}
 los_EL_shares %>%
 filter(Year == 2020, Seg == 2) %>% plot_los()

```

### Trips Paying
```{r}
 los_paying %>%
 filter(Year == 2020, Seg == 2) %>% plot_los()

```



Column
-------------------------------------
    
### 2020: Old Policy Segment 2: Anderson

```{r old_policy_2020_seg2}
old_policy_2020_seg2

```


### 2020: New Policy Segment 2: Anderson

```{r new_policy_2020_seg2 }
new_policy_2020_seg2

```


Year 2040: Sugarwood {data-navmenu="LOS"} 
=====================================

```{r 2040 V/C LOS plots, message=FALSE}

# old policy 2040 seg 1
df_old_policy_2040_seg1 <- df %>% 
              filter(Year == 2040, Policy == "oldPolicy", Seg == 1) %>%
              select(Hour, GU_NB_VC_RATIO, GU_SB_VC_RATIO, 
                     EL_NB_VC_RATIO, EL_SB_VC_RATIO)

old_policy_2040_seg1 <- df_old_policy_2040_seg1 %>% 
              gather( -Hour, key = direction, value = VC) %>%
              select(Hour, direction, VC ) %>% 
              plot_voc()


# old policy 2040 seg 2
df_old_policy_2040_seg2 <- df %>% 
              filter(Year == 2040, Policy == "oldPolicy", Seg == 2) %>%
              select(Hour, GU_NB_VC_RATIO, GU_SB_VC_RATIO, 
                     EL_NB_VC_RATIO, EL_SB_VC_RATIO)

old_policy_2040_seg2 <- df_old_policy_2040_seg2 %>%
              gather( -Hour, key = direction, value = VC) %>%
              select(Hour, direction, VC ) %>% 
              plot_voc()


# new policy 2040 seg 1
df_new_policy_2040_seg1 <- df %>% 
              filter(Year == 2040, Policy == "newPolicy", Seg == 1) %>%
              select(Hour, GU_NB_VC_RATIO, GU_SB_VC_RATIO, 
                     EL_NB_VC_RATIO, EL_SB_VC_RATIO) 

new_policy_2040_seg1 <- df_new_policy_2040_seg1 %>%
              gather( -Hour, key = direction, value = VC) %>%
              select(Hour, direction, VC ) %>% 
              plot_voc()


# new policy 2040 seg 2
df_new_policy_2040_seg2 <- df %>% 
              filter(Year == 2040, Policy == "newPolicy", Seg == 2) %>%
              select(Hour, GU_NB_VC_RATIO, GU_SB_VC_RATIO, 
                     EL_NB_VC_RATIO, EL_SB_VC_RATIO)  

new_policy_2040_seg2 <- df_new_policy_2040_seg2  %>%            
              gather( -Hour, key = direction, value = VC) %>%
              select(Hour, direction, VC ) %>% 
              plot_voc()
```

Column {data-width=350}
-------------------------------------
### Level of Service (LOS) 

* LOS A: V/C below 0.3
* LOS B: V/C between 0.3 and 0.5
* LOS C: V/C above 0.5

### EL Volumes
```{r}
 los_EL %>%
 filter(Year == 2040, Seg == 1) %>% plot_los()

```

### EL Shares
```{r}
 los_EL_shares %>%
 filter(Year == 2040, Seg == 1) %>% plot_los()

```

### Trips Paying
```{r}
 los_paying %>%
 filter(Year == 2040, Seg == 1) %>% plot_los()

```

Column 
-------------------------------------
    
### 2040: Old Policy Segment 1: Sugarwood

```{r old_policy_2040_seg1}
old_policy_2040_seg1
```


### 2040: New Policy Segment 1: Sugarwood

```{r new_policy_2040_seg1 }
new_policy_2040_seg1

```



Year 2040: Anderson {data-navmenu="LOS"} 
=====================================

Column {data-width=350}
-------------------------------------
### Level of Service (LOS) 

* LOS A: V/C below 0.3
* LOS B: V/C between 0.3 and 0.5
* LOS C: V/C above 0.5

### EL Volumes
```{r}
 los_EL %>%
 filter(Year == 2040, Seg == 2) %>% plot_los()

```

### EL Shares
```{r}
 los_EL_shares %>%
 filter(Year == 2040, Seg == 2) %>% plot_los()

```

### Trips Paying
```{r}
 los_paying %>%
 filter(Year == 2040, Seg == 2) %>% plot_los()

```


Column 
-------------------------------------

### 2040: Old Policy Segment 2: Anderson

```{r old_policy_2040_seg2}
old_policy_2040_seg2

```


### 2040: New Policy Segment 2: Anderson

```{r new_policy_2040_seg2 }
new_policy_2040_seg2

```


