---
title: "LOS_By_Segments"
author: "Amar Sarvepalli"
date: "September 7, 2017"
output: 
    flexdashboard::flex_dashboard:
---



```{r}
plot_ymax <- df %>% 
             group_by(Year) %>% 
             summarize(GU_max = max(GU_SB_VOL, GU_NB_VOL), 
                       EL_max = max(EL_SB_VOL, EL_NB_VOL))

ymax_2020_GL <- plot_ymax %>% filter(Year == 2020) %>% select("GU_max") %>% round(-3)
ymax_2020_EL <- plot_ymax %>% filter(Year == 2020) %>% select("EL_max") %>% round(-3)
ymax_2040_GL <- plot_ymax %>% filter(Year == 2040) %>% select("GU_max") %>% round(-3) 
ymax_2040_EL <- plot_ymax %>% filter(Year == 2040) %>% select("EL_max") %>% round(-3)

```

Year 2020 {data-navmenu="EL Volumes"}   
=====================================
Row
-------------------------------------
    
### 2020: EL Old Policy 
    Old Policy Definition: Where LOS-A is charged

```{r Old policy 2020, include=TRUE}
old_policy_2020 <- df %>%
              filter(Year == 2020, Policy == "oldPolicy") %>%
              select(Seg, Hour, EL_SB_VOL, EL_NB_VOL ) %>%
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>%
              plot_volumes(ymax_2020_EL,FALSE)

# Plot Old Polciy Volumes
old_policy_2020

# tmpFile <- tempfile(fileext = ".png")
export(old_policy_2020, paste0(dir_path,"/Output_Graphs/el_old_policy_2020.png"))
htmlwidgets::saveWidget(old_policy_2020, paste0(dir_path,"/Output_Graphs/el_old_policy_2020.html"))

```

Row
-------------------------------------
### 2020: EL New Policy
    New Policy Definition: Where LOS-A is NOT charged
```{r New policy 2020}
# Plot New Policy Volumes
new_policy_2020 <- df %>%
              filter(Year == 2020, Policy == "newPolicy") %>%
              select(Seg, Hour, EL_SB_VOL, EL_NB_VOL ) %>%
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>%
              plot_volumes(ymax_2020_EL,FALSE)

new_policy_2020
export(new_policy_2020, paste0(dir_path,"/Output_Graphs/el_new_policy_2020.png"))
htmlwidgets::saveWidget(new_policy_2020, paste0(dir_path,"/Output_Graphs/el_new_policy_2020.html"))
```



Year 2040 {data-navmenu="EL Volumes"}   
=====================================
Row
-------------------------------------
    
### 2040: EL Old Policy 
    Old Policy Definition: Where LOS-A is charged    
```{r Old policy 2040}
old_policy_2040 <- df %>% 
              filter(Year == 2040, Policy == "oldPolicy") %>%
              select(Seg, Hour, EL_SB_VOL, EL_NB_VOL ) %>% 
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>% 
              plot_volumes(ymax_2040_EL,FALSE)

# Plot Old Policy Volumes
old_policy_2040
export(old_policy_2040, paste0(dir_path,"/Output_Graphs/el_old_policy_2040.png"))
htmlwidgets::saveWidget(old_policy_2040, paste0(dir_path,"/Output_Graphs/el_old_policy_2040.html"))

```
   
Row
-------------------------------------
### 2040: EL New Policy 
    New Policy Definition: Where LOS-A is NOT charged 
```{r New policy 2040}
# Plot New Policy Volumes
new_policy_2040 <- df %>% 
              filter(Year == 2040, Policy == "newPolicy") %>%
              select(Seg, Hour, EL_SB_VOL, EL_NB_VOL ) %>% 
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>%
              plot_volumes(ymax_2040_EL,FALSE)

new_policy_2040 
export(new_policy_2040, paste0(dir_path,"/Output_Graphs/el_new_policy_2040.png"))
htmlwidgets::saveWidget(new_policy_2040, paste0(dir_path,"/Output_Graphs/el_new_policy_2040.html"))

```



Year 2020 {data-navmenu="GL Volumes"}   
=====================================
Row
-------------------------------------
    
### 2020: GL Old Policy 
    Old Policy Definition: Where LOS-A is charged

```{r GL Old policy 2020}
old_policy_2020 <- df %>%
              filter(Year == 2020, Policy == "oldPolicy") %>%
              select(Seg, Hour, GU_SB_VOL, GU_NB_VOL ) %>%
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>%
              plot_volumes(ymax_2020_GL,TRUE)

# Plot Old Polciy Volumes
old_policy_2020
export(old_policy_2020, paste0(dir_path,"/Output_Graphs/gl_old_policy_2020.png"))
htmlwidgets::saveWidget(old_policy_2020, paste0(dir_path,"/Output_Graphs/gl_old_policy_2040.html"))

```

Row
-------------------------------------
### 2020: GL New Policy
    New Policy Definition: Where LOS-A is NOT charged
```{r GL New policy 2020}
# Plot New Policy Volumes
new_policy_2020 <- df %>%
              filter(Year == 2020, Policy == "newPolicy") %>%
              select(Seg, Hour, GU_SB_VOL, GU_NB_VOL ) %>%
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>%
              plot_volumes(ymax_2020_GL,TRUE)

new_policy_2020
export(new_policy_2020, paste0(dir_path,"/Output_Graphs/gl_new_policy_2020.png"))
htmlwidgets::saveWidget(old_policy_2020, paste0(dir_path,"/Output_Graphs/gl_new_policy_2020.html"))

```



Year 2040 {data-navmenu="GL Volumes"}   
=====================================
Row
-------------------------------------
    
### 2040: GL Old Policy 
    Old Policy Definition: Where LOS-A is charged    
```{r GL Old policy 2040}
old_policy_2040 <- df %>% 
              filter(Year == 2040, Policy == "oldPolicy") %>%
              select(Seg, Hour, GU_SB_VOL, GU_NB_VOL ) %>% 
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>% 
              plot_volumes(ymax_2040_GL,TRUE)

# Plot Old Policy Volumes
old_policy_2040
export(old_policy_2040, paste0(dir_path,"/Output_Graphs/gl_new_policy_2040.png"))
htmlwidgets::saveWidget(old_policy_2040, paste0(dir_path,"/Output_Graphs/gl_new_policy_2040.html"))


```
   
Row
-------------------------------------
### 2040: GL New Policy 
    New Policy Definition: Where LOS-A is NOT charged 
```{r GL New policy 2040}
# Plot New Policy Volumes
new_policy_2040 <- df %>% 
              filter(Year == 2040, Policy == "newPolicy") %>%
              select(Seg, Hour, GU_SB_VOL, GU_NB_VOL ) %>% 
              gather(-Seg, -Hour, key = direction, value = Volume) %>%
              mutate(Segment = paste0("Seg ", Seg, direction)) %>%
              select(Segment, Hour, Volume ) %>% 
              plot_volumes(ymax_2040_GL,TRUE)

new_policy_2040
export(new_policy_2040, paste0(dir_path,"/Output_Graphs/gl_new_policy_2040.png"))
htmlwidgets::saveWidget(new_policy_2040, paste0(dir_path,"/Output_Graphs/gl_new_policy_2040.html"))
```


